Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
rebuttal comments
final?

	We thank the reviewers for their comments.

@@

%\paragraph{Review $\#$32: Why would the chair give up control of choosing the winner?”.}
\textit{\textbf{}}
%Specifying general algorithms is demanding, hence, we adapt a mechanism used in a real life experiment by Giritligil et al. [2005] in a novel way for the setting of elicitation of positioning scoring rules (PSRs).

@@

\textit{\textbf{Is Figure 1 for the synthetic data? Please specify. Why is Figure 2 shown for only Pessimistic, not all the approaches?}}

@@

Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5. We designed several strategies in order to challenge one another and select the best strategy in the most challenging setting (Impartial Culture). Once this was found to be Pessimistic, we tested it on real dataset.

>>>>

	We thank the reviewers for their comments. We address factual errors ($\#$2) and both factual errors and direct questions ($\#$32 and $\#$56).

@@

%\paragraph{Review $\#$32: Why would the chair give up control of choosing the winner?”.}
%Specifying general algorithms is demanding, hence, we adapt a mechanism used in a real life experiment by Giritligil et al. [2005] in a novel way for the setting of elicitation of positioning scoring rules (PSRs).

@@

%\paragraph{Review $\#$32 "Is Figure 1 for the synthetic data? Please specify. (…) Why is Figure 2 shown for only Pessimistic, not all the approaches?"}

@@

%Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5. We designed several strategies in order to challenge one another and select the best strategy in the most challenging setting (Impartial Culture). Once this was found to be Pessimistic, we tested it on real dataset.
